---
title: "Data products project"
author: "Gouthami Senthamaraikkannan"
date: "May 11, 2016"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is a presentation depicting an app that predicts the enginer displacement of a car, given its mileage and no. of cylinders.

i.e., the regressors considered in the model are

- City mileage (gallons)
- Highway mileage (gallons)
- No. of cylinders

and the output is

- Enginer displacement

## What the app does

The regression model used for prediction is based on the "mpg" dataset released by EPA. All the variables in the data set are shown below.

```{r summ, echo=FALSE}
library(ggplot2)

data("mpg")
colnames(mpg)
```

## Correlation between regressors and regressand

The following gives an idea of the correlation that exists mileage, no. of cylinders and the regressand, engine displacement.

```{r pressure, echo= FALSE}
library(corrplot)
library(dplyr)

mpg_r <- mpg[, c('displ', 'hwy', 'cty', 'cyl')]
M <- cor(mpg_r)
corrplot(M, method = 'circle')
```

## Linear model
```{r model, echo = TRUE}
m <- lm(displ~hwy+cty+cyl, data = mpg)
m
```

## Prediction using the linear model
```{r pred, echo=TRUE}
hwy <- 7
cty <- 5
cyl <- 4
d <- data.frame(hwy, cty, cyl)
p <- predict(m, d)
```

Thus, the predicted engine displacement for the given values of hwy, cty & cyl is 
```{r prv, echo = TRUE}
p
```
